\documentclass{article}

\usepackage[hmargin=1.25cm, vmargin=0.75cm]{geometry}
\usepackage[colorlinks]{hyperref}
\usepackage{relsize}
\usepackage{enumitem}
\usepackage{fontspec}

\setmainfont[Path=fnt/lato/, BoldItalicFont=*-BoldItalic.ttf, BoldFont=*-Bold.ttf, ItalicFont=*-LightItalic.ttf, UprightFont=*-Light.ttf]{Lato}
\setsansfont[Path=fnt/lato/, BoldItalicFont=*-Italic.ttf, BoldFont=*-Regular.ttf, ItalicFont=*-ThinItalic.ttf, UprightFont=*-Thin.ttf]{Lato}

\makeatletter
\newcommand\fsc[1]{\@fsc@a#1 \relax\relax}
\def\@fsc@a#1 #2\relax{\@fsc@b#1\relax\relax\if\relax#2\relax\else\ \@fsc@a#2\relax\fi}
\def\@fsc@b#1#2\relax{%
\ifnum`#1=\lccode`#1\relax%
\textsmaller[1]{\char\uccode`#1}%
\else%
\textlarger[0]{#1}\fi%
\ifx\relax#2\relax\else\@fsc@b#2\relax\fi%
}
\let\@old@itemize\itemize%
\let\@old@enditemize\enditemize%
\renewenvironment{itemize}{\@old@itemize[leftmargin=*]\relax}{\@old@enditemize}
\makeatother

\newcommand{\namesection}[3]{
\hfill{
\fontsize{40pt}{60pt}
\fontspec[Path=fnt/lato/]{Lato-Thin.ttf}\selectfont #1 %
\fontspec[Path=fnt/lato/]{Lato-Regular.ttf}\selectfont #2%
}
\vskip5pt
\hfill{\fontspec[Path=fnt/lato/]{Lato-Thin.ttf}\fontsize{11pt}{14pt}\selectfont #3}\par
\noindent\makebox[\linewidth]{\rule{0.9\paperwidth}{0.4pt}}
\vspace{5pt}
}

\newcommand{\contents}[2]{%
\begin{minipage}[t]{0.62\textwidth}#1\end{minipage}%
\hfill%
\begin{minipage}[t]{0.32\textwidth}#2\end{minipage}
}

\let\oldsection\section
\renewcommand{\section}[2]{%
\oldsection*{%
\fontspec[Path=fnt/lato/]{Lato-Bold.ttf}\fontsize{16pt}{16pt}\selectfont\bfseries\fsc{#1}\normalfont%
}
#2
}

\newcommand{\resumeitem}[3]{%
\par\fontspec[Path=fnt/lato/]{Lato-Bold.ttf}\fontsize{12pt}{12pt}\selectfont\bfseries\fsc{#1}\normalfont\ | %
\fontspec[Path=fnt/lato/]{Lato-Light.ttf}\fontsize{12pt}{12pt}\selectfont\bfseries{#2}\normalfont%
\par%
#3%
\vspace{5pt}%
}

\begin{document}

\namesection{Behrooz}{Vedadian}{%
\href{https://github.com/vedadian}{Github} | \href{https://www.linkedin.com/in/behrooz-vedadian/}{LinkedIn} | \href{mailto:vedadian@gmail.com}{vedadian at gmail dot com}
}

\contents{% Left column

\section{Skills}{%
\resumeitem{Programming}{C++, Python, $\lambda$-calculus, Javascript}{}%{See \href{https://github.com/vedadian}{github.com/vedadian}}%
\resumeitem{Deep Learning Toolkits}{PyTorch, Tensorflow, \textasciitilde{JAX}, HuggingFace Transformers}{}%{See \href{https://github.com/vedadian}{github.com/vedadian}}%
\resumeitem{Deep Learning Foundations}{Linear algebra, Convex Optimization, Measure theory, Modern statistics, Matrix Calculus}{}%{See \href{https://github.com/vedadian}{github.com/vedadian}}%
\resumeitem{Frontend}{Qt, Vanilla HTML+CSS+JS, ReactJS}{}%{See \href{https://vedadian.com}{vedadian.com}}%
}

\section{Experience}{
\resumeitem{Researcher and Senior Software Engineer}{Targoman Intelligent Processing Co. Pjc. (2015-Present)}{%
\begin{itemize}
  \item Development of a neural machine translation engine based on Marian-NMT toolkit (C++)
  \item Development of a PDF layout analysis engine from scratch (Javascript \& WASM)
  \item Development of a lightweight fast API server for neural machine translation engine on top of libevent (C++)
\end{itemize}
I co-founded Targoman with my supervisor and one of the lab colleges. Our main end-user software can be examined at \href{https://tarjomyar.ir/test.html}{https://tarjomyar.ir/test.html}
}
\resumeitem{Researcher and Senior Software Engineer}{HLT Lab \@ AmirKabir Univ. of Tech. (2013-2015)}{%
\begin{itemize}
  \item Development of a text processing library for Persian (C++)
  \item Development of a robust statistical translation engine (C++)
\end{itemize}
Resulting software and libraries can be found in \href{https://github.com/targoman}{Targoman's github}
}
\resumeitem{Researcher and Senior Software Engineer}{Hoda System Co. Ltd. (2009-2014)}{%
\begin{itemize}
  \item Implementation of a convolution based OCR system for extracting Egyptian ID card information for Egypt City Bank using OpenCV (C++)
  \item Implementation of multilayer perceptron using Intel MKL (C++)
\end{itemize}
}
\resumeitem{Teacher's Assistant}{Computer Programming Course}{%
at Sharif University of Technology (in 2001)
}
\resumeitem{Teacher's Assistant}{Statistical Natural Language Processing}{%
at AmirKabir University of Technology (in 2014)
}
}

}{% Right column
\section{Honors}{
\textbf{\fsc{National Computer Prog. Content}}
\begin{itemize}
  \item Randked $5^{th}$ in 1997
  \item Randked $3^{rd}$ in 1998
\end{itemize}

\textbf{\fsc{National Ph.D. Entrance Exam.}}
\begin{itemize}
  \item Ranked $9^{th}$ in 2013
\end{itemize}
}
\section{Education}{
\textbf{Ph.D} | {AmirKabir Univ. of Tech.}
\par Computer Engineering
\par Artificial Intelligence
\par ``Learning sequence to sequence maps by incorporating embedded input structure in deep networks for machine translation''
\par \textit{Dr. Shahram Khadivi \& Dr. Mohammad Rahmati}

\textbf{M.Sc} | {AmirKabir Univ. of Tech.}
\par Electrical Engineering
\par Communication Systems
\par ``Signal Detection in Nonstationary Environments using Wavelets''
\par \textit{Dr. Hamidreza AminDavar}

\textbf{B.Sc} | {Sharif Univ. of Tech.}
\par Electrical Engineering
\par Electronics
\par ``Speaker Identification using Hidden Markov Models''
\par \textit{Dr. Mohammad Nayebi}

\textbf{Diploma} | {National Organization of Developement of Exceptional Talents}
\par Mathematics \& Physics

}
}
\vskip15pt
\hfill{Last updated \today}
\end{document}
